Incentivizing Exploration with Unbiased Histories

### 2019-02-01 COLT 2019 Submission/2level.tex
Minor edits to save space.

We prove that for a constant number of arms, with constant probability, a full-disclosure path of constant length suffices to sample each arm at least once. We will build on this fact throughout.

@@

We provide a simple disclosure policy based on full-disclosure paths. The policy follows the ``explore-then-exploit'' paradigm. The ``exploration phase" comprises the first $N = T_1\cdot \fdpL$ rounds, and consists of $T_1$ full-disclosure paths of length $\fdpL$ each, where $T_1$ is a parameter. In the ``exploitation phase", each agent $t>N$ receives the full subhistory from exploration, \ie $m_t = \SubH{[N]}$. The info-graph for this disclosure policy is shown in Figure~\ref{fig:2level}.

@@

The proofs can be found in Appendix~\ref{app:warmup}. One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$. Indeed, this number, denoted $\fdpN$, is the same for all such paths. Then,

>>>>

We prove that for a constant number of arms, with constant probability, a full-disclosure path of constant length suffices to sample each arm once. We use this fact throughout.

@@

We provide a simple disclosure policy based on full-disclosure paths. The policy follows the ``explore-then-exploit'' paradigm. The ``exploration phase" comprises the first $N = T_1\cdot \fdpL$ rounds, and consists of $T_1$ full-disclosure paths of length $\fdpL$ each, where $T_1$ is a parameter. In the ``exploitation phase", each agent $t>N$ receives the full subhistory from exploration, \ie $m_t = \SubH{[N]}$. The info-graph for this disclosure policy is in Figure~\ref{fig:2level}.

@@

The proofs can be found in Appendix~\ref{app:warmup}. One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$. Indeed, this number, denoted $\fdpN$, is the same for all such paths.

### 2019-02-01 COLT 2019 Submission/3level.tex
Minor edits to save space.

\xhdr{The ``good events".}
We establish four ``good events" each of which occurs with high probability.
\begin{description}
\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects at least $\Omega(T_1)$ samples of each arm.
\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than its actual mean and other arms look worse than their actual means.
\item[(\event{4})] \emph{Concentration in prefix:}
The empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls. (This ensures accurate reward estimates in exploitation.)
\end{description}

@@

\xhdr{Case analysis.}
We now proceed to bound the regret conditioned on the four ``good events". W.l.o.g., assume $\mu_1 \geq \mu_2$. We break down the regret analysis into four cases, based on the magnitude the gap parameter $\Delta = \mu_1-\mu_2$. As a shorthand, denote
    $\conf{n} = \sqrt{\log(T)/n}$.
In words, this is a confidence term, up to constant factors, for $n$ independent random samples.

The simplest case is very small gap, which trivially yields an upper bound on regret.

@@

Another simple case is when $\Delta$ is sufficiently large, so that
the data collected in any first-level group suffices to determine the best arm. The proof follows from \event{1} and \event{2}.

>>>>

\xhdr{The ``good events".}
We establish four ``good events" each of which occurs with high probability.
\begin{description}
\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects  $\Omega(T_1)$ samples of each arm.
\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than its actual mean and other arms look worse than their actual means.
\item[(\event{4})] \emph{Concentration in prefix:}
Empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls (ensuring accurate reward estimates in exploitation.)
\end{description}

@@

\xhdr{Case analysis.}
We now proceed to bound the regret conditioned on the four ``good events". W.l.o.g., assume $\mu_1 \geq \mu_2$. We break down the regret analysis into four cases, based on the magnitude the gap parameter $\Delta = \mu_1-\mu_2$. As a shorthand, 
    $\conf{n} = \sqrt{\log(T)/n}$.
In words, this is a confidence term, up to constant factors, for $n$ independent random samples.
The simplest case is very small gap, which trivially yields an upper bound on regret.

@@

The second case is when $\Delta$ is sufficiently large, so that
the data collected in any first-level group suffices to determine the best arm. The proof follows from \event{1} and \event{2}.

### 2019-02-01 COLT 2019 Submission/llevel-overview.tex
remove fullpage
Minor edits to save space.

\section{$\tilde O(\sqrt{T})$ regret with $L$-level policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our three-level
policy to a more adaptive $L$-level policy for $L > 3$ in order to
achieve a regret rate of $O_K(\sqrt{T} \polylog(T))$. We provide two
such policies. The first policy achieves the root-$T$ regret rate with
$O(\log \log T)$ levels.

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}

>>>>

\section{$\tilde O(\sqrt{T})$ regret with $L$-level policy}
\label{sec:llevel}

We give an overview of how we extend our three-level
policy to a more adaptive $L$-level policy for $L > 3$ in order to
achieve a regret rate of $O_K(\sqrt{T} \polylog(T))$. We provide two
such policies. The first policy achieves the root-$T$ regret rate with
$O(\log \log T)$ levels.

@@

\begin{figure}[h]
\centering
\begin{tikzpicture} [scale = 0.9]
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}
